---
title: "R Notebook"
output: html_notebook
---

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
print("Part 3")
```

```{r}
train = read.csv("train.csv", header = T)
test = read.csv("test.csv", header = T)
```

```{r}
head(train)
```


```{r}
#Add a "Survived" variable to the test set to allow for combining data sets
test.survived = data.frame(survived = rep("None",nrow(test)), test[,])
```


```{r}
# Combine the data sets
data.combined = rbind(train, test.survived)
```

```{r}
# Check the data type
str(data.combined)
```

```{r}
# survived and pclass is not int and str so lets convert to as.factor
data.combined$survived = as.factor(data.combined$survived)
data.combined$pclass = as.factor(data.combined$pclass)
```
```{r}
# Lets Look at Gross survival rate
table(data.combined$pclass)
```



```{r}
# Load GGPlot library for visualization
library("ggplot2")

```

```{r}
# Hypothesis Rich Folk survived at a higher rate
train$pclass = as.factor(train$pclass)
ggplot(train, aes(x = pclass, fill = factor(survived))) +
  geom_bar() +
  xlab("Pclass") + 
  ylab("Total Count") +
  labs(fill = "Survived")

```
```{r}
# Examine the first few names in the training data set
head(as.character(train$name))
```

```{r}
# Check how many Unique names are there in train & test sets?
length(unique(as.character(data.combined$name)))
```
```{r}
nrow(data.combined$name)
```
```{r}
# Two duplicate names take a closure look
# First, get the duplicate names and store them as a vector
dup.names = as.character(data.combined[which(duplicated(as.character((data.combined$name)))),"name"])

```
```{r}
# Next, take a look at the records in the combined data set
data.combined[which(data.combined$name %in% dup.names),]
```


```{r}
# What is up with "Miss." and "Mr."  thing
library(stringr)
```



```{r}
  # Any Correlation with 
```

